TEM-t as The Universal Neural Computer

### 2024-06-06 neural-computer-neurips/paper_neurips.tex
Adding several references
added intro

@@

@@

@@

% ###################################################################################################################
% ###################################################################################################################
% Adding a Single big Image
% ###################################################################################################################
% ###################################################################################################################
\section{Single image}

@@

% ###################################################################################################################
% ###################################################################################################################
% Adding multiple Images
% ###################################################################################################################
% ###################################################################################################################
\section{Multiple images}

@@

% ###################################################################################################################
% ###################################################################################################################
% Example of Citations
% ###################################################################################################################
% ###################################################################################################################
\section{Citations}

Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed eiusmod tempor incidunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquid ex ea commodi consequat. Quis aute iure reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint obcaecat cupiditat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum. 
For example, \cite{reference_1} or \cite{reference_2} and \cite{reference_3} anre example for citations.

% ###################################################################################################################
% ###################################################################################################################
% Tables
% ###################################################################################################################
% ###################################################################################################################
\section{Tables}

@@

\section{Conclusions}

@@

\subsubsection*{Acknowledgments}

@@

>>>>

% #########################################################################################
% #########################################################################################
% Abstract
% #########################################################################################
% #########################################################################################

@@

% #########################################################################################
% #########################################################################################
% Introduction
% #########################################################################################
% #########################################################################################

@@

\cite{beiran2023parametric}

(Must do a paper dump showcasing some advancements)
In the last few decades we have seen many advancements in neuroscience. It is now possible to record activity from every neuron in a zebrafish larva’s brain while it is freely swimming and responding to stimuli (Kim et al. 2017). We have a nearly complete map of one hemisphere of the fly brain, with every neuron and most of its synapses accounted for (Pipkin 2020). The neurons responsible for a mouse’s memory of an event can be recorded, tagged, and replayed by laser stimulation, causing the mouse to behave as if the event had happened again (CarrilloReid et al. 2019; Ramirez et al. 2013). (This references can be found on John M Beggs - The Cortex and the Critical Point)

Such advancements brought to light evidence for what was once only a theory, for example, Tolman (1948) argued that for Humans and other animals to make complex inferences from sparse observations and rapidly integrate new knowledge to control their behavior there should exist a systematic organization of such knowledge on what could be called a cognitive map. (note, try to make it sound like the theory of computing - references can be found on the TEM paper)

The combination of all these technological and theoretical developments demonstrated through evidence and theoretical models that there is indeed a mechanistic basis for memory formation, this was shown in the Nobel winning work done by May-Britt Moser, Edvard I. Moser (reference the nobel prize)(Nobel prize winning Place Cells, Grid Cells, and Memory). This work has inspired new theories in theoretical-neuroscience that proposes the idea that relational memory and spatial reasoning might be related by a common mechanism (Eichenbaum and Cohen, 2014 - found in the TEM paper). (need to work on this paragraph)

Limited evidence provided in recent work with grid cells has shown, there is mechanism generating invariant representations, by using simultaneous recordings from many hundreds of grid cells and subsequent topological data analysis that the joint activity of grid cells from an individual module (neuronal population) resides on a toroidal manifold as expected in a two-dimensional CAN (Continuous Attractor Network). The positions are maintained between environments and from wakefulness to sleep, demonstrating to be invariant representations. This research demonstrated ,with some limitations, network dynamics on a toroidal manifold and provided a population-level visualization of CAN dynamics in grid cells.
(reference Toroidal topology of population activity in grid cells)

Even though the limitations

There is growing evidence to support that manifolds maintain a well-preserved covariance across tasks. These results support the view that complex computation emerges from the flexible activation of different combinations of “Neural modes” (Need to find a better term) which themselves arise from the Network Connectivity (reference to Hopfield is all you need and Transformers) (Cortical population activity within a preserved neural manifold underlies multiple motor behaviors, reference 8 for Emergence of universal computations through neural manifold dynamics)

In this paper we want to show that there exists a morphism between Neuroscience models and existing NN models, so we can approximately represent the Neural Manifolds with the Transformers.

Must note that we are not saying the brain is closely related to transformers, instead we are  using a mathematical relationship between the so popular transformers and the attractor neural networks that have been carefully formulated in neuroscience models as being an essential piece in forming invariant representations in a topological structure that facilitates the emergence of Computation Through Neural Population Dynamics.
Additionally, by using a modified transformers model we can leverage several tools, techniques, software and hardware that have been matured and extensively tested given the popularity and widespread use of transformers. Further studies are required to develop and validate a better architecture that better represents Neural Population Dynamics.

@@

% #########################################################################################
% #########################################################################################
% Theory of Computing
% #########################################################################################
% #########################################################################################

\section{Theory of Computing}

Computing is not a new concept, there is historical evidence that the Greeks were already capable of performing computation to predict the astronomical movements giving a programmable input (Antikythera mechanism).

% #########################################################################################
% #########################################################################################
% Example - Adding a Single big Image
% #########################################################################################
% #########################################################################################

\section{Single image}

@@

% #########################################################################################
% #########################################################################################
% Example - Adding multiple Images
% #########################################################################################
% #########################################################################################

\section{Multiple images}

@@

% #########################################################################################
% #########################################################################################
% Example - Citations
% #########################################################################################
% #########################################################################################
\section{Some other Section}

Citations examples used to be here

% #########################################################################################
% #########################################################################################
% Example - Tables
% #########################################################################################
% #########################################################################################
\section{Tables}

@@

% #########################################################################################
% #########################################################################################
% Conclusion
% #########################################################################################
% #########################################################################################
\section{Conclusions}

@@

% #########################################################################################
% #########################################################################################
% Acknowledgments
% #########################################################################################
% #########################################################################################
\subsubsection*{Acknowledgments}

@@

% #########################################################################################
% #########################################################################################
% References
% #########################################################################################
% #########################################################################################
